---
title: "gtsummary in quarto"
execute:
  warning: false
format:
  html:
    theme: zephyr
echo: false
---

```{r}
#| echo: false
library(tidyverse)
library(gtsummary)
nlsy_cols <- c("glasses", "eyesight", "sleep_wkdy", "sleep_wknd", 
               "id", "nsibs", "samp", "race_eth", "sex", "region", 
               "income", "res_1980", "res_2002", "age_bir")
nlsy <- read_csv(here::here("data", "raw", "nlsy.csv"), 
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
                 skip = 1, col_names = nlsy_cols) |> 
  mutate(region_cat = factor(region, labels = c("Northeast", "North Central", "South", "West")),
         sex_cat = factor(sex, labels = c("Male", "Female")),
         race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic")),
         eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
         glasses_cat = factor(glasses, labels = c("No", "Yes"))) 
```

# Customization of `tbl_summary()`

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir),
  label = list(
    race_eth_cat ~ "Race/ethnicity",
    region_cat ~ "Region",
    eyesight_cat ~ "Eyesight",
    glasses ~ "Wears glasses",
    age_bir ~ "Age at first birth"
  ),
  missing_text = "Missing")
```

Exercise 2.2 Part 2

Adding code below.

```{r}
#| eval: false 
tbl_summary(
  NLSY,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

This is the corrected document.

```{r}
#| label: tbl-1
#| tbl-cap: "as_kable() table modified"
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir)) |>
  	as_kable()
  
totalsamples <- nrow(nlsy)
```

@tbl-1 : this is modified by a as_kable pipe. This is actually the `r 2+2` table in the documents.

This did not work. Will this work: First, `r nrow(nlsy)` and second, will this `r totalsamples` . Hope so.

```{r}
ds <- list(n = nrow(nlsy), 
					 mean_age = mean(nlsy$age_bir, na.rm = TRUE)
					 )
```

The data should give me `r ds$n` and mean age of `r ds$mean_age`.

**Next section, Inline text function**

```{r}
#| label: tbl-descr
#| tbl-cap: "Descriptive statistics"
#| output-location: slide
table1 <- tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir, sleep_wknd)) |> 
  add_overall(last = TRUE)
table1
```

Next is the code for the inline table.

```{r}
sleepnd <- inline_text(table1, variable = "sleep_wknd", column = "stat_1")
```

This shows the data for the inline test in the following `r sleepnd`.
